---
title: "Map visualization"
output:
  html_document:
    fig_cap: yes
    highlight: tango
    smooth_scroll: no
    theme: flatly
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Maps in [TALD](https://lingconlab.ru/tald) are generated automatically based on the **value** columns.

As explained in [Feature datasets](datasets.html), you can have multiple value columns in order to generate different maps. You can use both nominal and numeric values.

> Keep in mind that a large number of values is difficult to perceive, do not use more than 5 values on one map.

If you want, you can experiment with map visualizations by yourself using the `lingtypology` (see the [documentation](https://ropensci.github.io/lingtypology/)) and `RCaucTile` (see the [documentation](https://lingconlab.github.io/RCaucTile/)) packages for R. It is also possible to use the Python version named `PyCaucTile` (see the [documentation](https://lingconlab.github.io/PyCaucTile/)).

Here is the simple code that will visualise your data:

```{r, eval = FALSE}
library(tidyverse)
library(gsheet)
library(RCaucTile)

"link to your google sheet with data" |> 
  gsheet2tbl() |> 
  ec_tile_map(feature_column = "value1") # change to value2 if needed
```

